Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-16 paper/paper.tex
nudge Fig 4

\usepackage{algorithm}
\usepackage{amsfonts}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usepackage[justification=centering]{caption}
\usepackage{stmaryrd}
\usepackage{hhline}
\usepackage{pifont}
\usepackage{longtable}
\usepackage{afterpage}
\usepackage{wasysym}
\usepackage[scaled]{helvet}

@@

The second approach is illustrated in Figure~\ref{fig:CEGIS} and uses a
two-stage verification: the first stage performs potentially unsound
fixed-point operations assuming a plant precision \param{I_p}{F_p}, and the
second stage restores soundness by validating these operations
using interval arithmetic on the synthesized controller.
%
\begin{figure*}[htb]
\centering
\resizebox{.9\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=.6cm, column sep=2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=7cm,
	minimum height=1cm,
	label={\sc Verify},] (verif) {};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \node (gp) {\sf Closed-loop System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based Verifier};
   \node (fp)  at ([xshift=2cm]aux.center) {\sf Fixed-point \\\sf Arithmetic Verifier};
   }   
    \\
  };

@@

 \end{tikzpicture}
}
 \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (Step~D)
\label{fig:CEGIS}}
\end{figure*}
%
%
In more detail, in the first stage, denoted by {\sc Uncertainty} in Figure~\ref{fig:CEGIS}, 
assuming a precision \param{I_p}{F_p} 
we check whether the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_\mathit{stability}$ is satisfiable for $S(z)$.
If this is the case, then we obtain a counterexample 
$\tilde G(z)$, 
%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which makes the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesize} phase, 
we obtain a candidate solution consisting 
of a controller $C(z)$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.

>>>>

\usepackage{algorithm}
\usepackage{amsfonts}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}
\usepackage[justification=centering]{caption}
\usepackage{stmaryrd}
\usepackage{hhline}
\usepackage{pifont}
\usepackage{longtable}
\usepackage{afterpage}
\usepackage{wasysym}
\usepackage[scaled]{helvet}

@@

The second approach is illustrated in Figure~\ref{fig:CEGIS} and uses a
two-stage verification: the first stage performs potentially unsound
fixed-point operations assuming a plant precision \param{I_p}{F_p}, and the
second stage restores soundness by validating these operations
using interval arithmetic on the synthesized controller.
%
\begin{figure*}[htb]
\centering
\resizebox{.9\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=.6cm, column sep=2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=7cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify},] (verif) {};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \node (gp) {\sf Closed-loop System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based Verifier};
   \node (fp)  at ([xshift=2cm]aux.center) {\sf Fixed-point \\\sf Arithmetic Verifier};
   }   
    \\
  };

@@

 \end{tikzpicture}
}
\caption{Counterexample-Guided Inductive Synthesis of Closed-loop Systems (Step~D)
\label{fig:CEGIS}}
\end{figure*}
%
%
In more detail, in the first stage, denoted by {\sc Uncertainty} in Figure~\ref{fig:CEGIS}, 
assuming a precision \param{I_p}{F_p} 
we check whether the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_\mathit{stability}$ is satisfiable for $S(z)$.
If this is the case, then we obtain a counterexample 
$\tilde G(z)$, 
%denoted by values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which makes the closed-loop system unstable. 
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesize} phase, 
we obtain a candidate solution consisting 
of a controller $C(z)$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.
